\chapter*{Acknowledgement}


First of all, I would like to express my sincere gratitude to my advisor Dominik~Kwietniak. 
%
I have been extremely lucky to have a supervisor who cared so much about my work.
%
His friendly guidance and expert advice have been invaluable throughout  the entire period of our collaboration. 
%
Without his support and encouragement, I would not have been able to complete this thesis.


I am also pleased to say thank you to Professor Klaudiusz Wójcik for the support he granted me during all years of my Ph.D. studies.

The completion of my dissertation would not have been possible without Martha Łącka, who has been my closest research partner and a true friend. 

I thank Jakub Byszewski for his enthusiasm, many constructive discussions, and helpful advice.

I would also like to extend my gratitude to Łukasz Kosiński and Sylwester Zając, whose guidance and support I experienced in the very early stages of my research.

I would always remember my friends: Jakub Tarnawski, Andrzej Pezarski, Olena Karpel, Michał Świętek, Weronika Czerniawska, Paweł Potorski, and Maria Dudek. 
%
I am grateful for their encouragement and the fun-time we spent together. I also thank Pierre Guillon for his kindness and motivation.

I would not be where I am today without the support and encouragement of my parents, grandmother, and sister. They always believed in me like no one else ever had.

In the end, I would like to thank my husband Damian for his love and constant support. Not only he motivates me and keeps me going on, but he also serves me as an example of an excellent mathematician.